Considering scale in multilayer animal social networks

### 2020-08-26 paper/manuscript.Rmd
maybe add code availability?

>>>>

# Code Availability

Code for performing all multilayer social network analyses and generating the
figures is available at 
https://github.com/robitalec/scale-in-multilayer-networks [@Robitaille_2020] <!-- TODO: zenodo-->
and released under the GNU General Public License 3.0. We depended on numerous R
packages notably for the analysis: igraph, data.table, spatsoc, asnipe, and
grainchanger, for the figures: ggplot2 and patchwork, and for reproducibility
and workflow management drake, renv, and knitr.
